Seminar paper on Probabilistic Near-Duplicate Detection Using Simhash

### 2019-07-08 ii/paper/paper.tex
More progress

\section{Conventional Hashing}

@@

If, on the other hand, one's goal is to find near duplicates, which are identical for the most part, but sometimes only differ by a few bits or bytes, this hashing approach immediately becomes useless, due to this property.
Due to the need for a hashing algorithm, that creates a fingerprint based on the features and structure of the input data, \emph{Simhash} has been created.

@@

\emph{Simhash} is a procedure used to create a fingerprint of a any kind of data.
This fingerprint can then be used to, for instance, inspect two files for similarity.

@@

The size of available features can vary significantly and is completely in the hand of the designer for each \emph{Simhash} implementation.
It's important to note, that there exists no clear guideline on which features of a data set are interesting and which features can be ignored.
The performance of a \emph{Simhash} implementation thereby also depends on the chosen features and the respective properties of the dataset.
Such features can be for instance binary chunks, file extension~\cite{inproc:simhash}, individual words, tags or URLs~\cite{inproc:main}.

\begin{figure}[H]
\includegraphics[scale=0.5]{./gfx/binary_chunk_fingerprint}
\centering
\caption{Visual example for calculating a \emph{Simhash} fingerprint.
A binary file split into chunks, which are then hashed.
Combining all hashes results in the desired fingerprint.~\cite{article:sampling-similarity}}\label{fig:gitalizer-relationship}
\end{figure}

@@

Algorithm 1 explaines the process of~\cite{inproc:evaluation} for creating fingerprints.
At first one iterates over the features subset $F(u)$, which is selected from the set $F$ of all unique features with $F(u) \in F$.
Each feature is then uniformly hashed to a fix size.
This uniform hashing can be seen as a random projection of a arbitrarily large feature to a fixed size.
The amount of ones and zeros in this hash are then counted.
A one increments the counter, a zero decrements it.
The result is then stored in a vector $W$ which has the same length as $F(u)$ under the respective index of the feature.

After calculating all values for each feature, a new binary Vector $B$ will then be created with the same Length as $W$.
Each value $v_i \geq 0$ at index $i$ will result in $B[i] = 1$, while each $v_i < 0$ will reslut in $B[i] = 0$.

The next challenge, which is the main topic this paper deals with, is to compare a fingerprint to all other fingerprints inside the given dataset.

@@

\subsection{}

\subsection{Achievements of Session Juggler}

>>>>

\subsection{Conventional Hashing}

@@

If, on the other hand, one's goal is to find near duplicates, which are identical for the most part, but sometimes only differ by a few bits or bytes, this hashing approach immediately becomes useless, due to this property.
Due to the need for a hashing algorithm, that creates a fingerprint based on the features and structure of the input data, \emph{simhash} has been created.

@@

To compare documents for similarity a methodology to create some uniform value, which should be identical for two similar matching documents.

\emph{simhash} is a procedure used to create a fingerprint of a any kind of data.
This fingerprint can then be used to, for instance, inspect two files for similarity.

@@

The size of available features can vary significantly and is completely in the hand of the designer for each \emph{simhash} implementation.
It's important to note, that there exists no clear guideline on which features of a data set are interesting and which features can be ignored.
The performance of a \emph{simhash} implementation thereby also depends on the chosen features and the respective properties of the dataset.
Such features can be for instance binary chunks, file extension~\cite{inproc:simhash}, individual words, tags or URLs~\cite{inproc:main}.

\begin{figure}[H]
\includegraphics[scale=0.5]{./gfx/binary_chunk_fingerprint}
\centering
\caption{Visual example for calculating a \emph{simhash} fingerprint.
A binary file split into chunks, which are then hashed.
Combining all hashes results in the desired fingerprint.~\cite{article:sampling-similarity}}\label{fig:simhash-example}
\end{figure}

@@

Algorithm 1 explains the process of~\cite{inproc:evaluation} for creating fingerprints.
At first one iterates over the features subset $F(u)$ of size $b$, which is selected from the set $F$ of all unique features with $F(u) \in F$.
Each feature is then uniformly hashed to a fix size.
This uniform hashing can be seen as a random projection of a arbitrarily large feature to a fixed size.
The amount of ones and zeros in this hash are then counted.
A one increments the counter, a zero decrements it.
The result is then stored in a weight vector $W$ under the respective index of the feature. $W$ has the same length $b$.

After calculating all values of $W$, a new binary Vector $B$ will then be created with the same Length as $W$.
Each value $v$ with $v_i \geq 0$ at index $i$ will result in $B[i] = 1$, while each $v_i < 0$ will result in $B[i] = 0$.

@@

To achieve their goal of decreasing the runtime of fingerprint comparisons, the authors of~\emph{inproc:main} investigated the properties and distribution of weights of the temporary weight vector $W$ that was introduced the previous section.

For their current work, they used normalized term frequency–inverse document frequency (TF-IDF) weights.
This kind of weights is used to reflect the importance of a word to a document in a collection and is great for text-based document comparison methods~\cite{Salton:1986:IMI:576628}.
The corpus of the researchers consisted of 70M web pages.

\begin{figure}[H]
\includegraphics[scale=0.4]{./gfx/distribution.png}
\centering
\caption{Histogram of \emph{simhash} weights. A clear trend towards a Laplace-like distribution can be seen in a\).}\label{fig:weight-distribution}
\end{figure}

While using normalized TF-IDF weights, they noticed, that the distribution of weights rather resembles a Laplace-like distribution, than a Gaussian distribution, which has been expected, since the Central Limit theorem suggests it.
This can be seen in Figure~\ref{fig:weight-distribution}.

Using this knowledge they were able to generalize the formula for determining the specific weight of a feature to non-Bernoulli cases:

\[W_j(u) = \sum_{i \in F(u)} v_{ij}w_i(u)\]

$v$ is a vector, whose elements are drawn from a zero-mean symmetric distribution, which is theoretically equivalent to the Laplace-like distribution mentioned above.

After investigating the various probabilities and necessities for changing a weight to the side, it becomes apparent that certain bits are much more volatile to flip than others.
If one looks at the \emph{simhash} weights $(12, 0, -10)$, the second bit is much more likely to flip to the negative side, when small changes occur, than the other weights.
Much bigger changes would be needed to flip the weights at position 1 or 3.

\section{Bit order}

With the insight gained in the previous section, we are now able determine, which bits are more volatile to flip than others.
This knowledge can be utilized to determine an order, that should be used to determine the Hamming distance $h$ between the fingerprint and all hashes in the collection $D$.
While this is straight forward for single bit flips, where bits are simply ordered by their volatility, it becomes more complex, as soon as one wants to detect two-bit combination flips.

\subsection{Brute force}
